The Countercyclical Component of Capital Regulation

### 2020-05-10 Analysis/Draft/Draft_bookdown.Rmd
Several changes to the draft text. Version before I started the RW-lending project

To calculate measures of *Capital savings*, information on the distribution of banks' regulatory risk parameters is needed. I hand-collected information on the distribution of credit risk parameters from banks' Pillar-3 reports. As is common in the literature, I calculate *Capital savings* in terms of risk-weighted assets (RWA), which are simply capital requirements times 12.5, or risk-weights (RW), which are RWA divided by assets. The sample consists of 52 large banking groups that have adopted the IRB approach. The dataset covers 13 countries and goes from 2007 to 2018. Data at such granularity is not available in the common balance sheet datasets, and although very detailed, datasets from credit registers are restricted to one country, and may still lack the relevant information.

With this novel dataset, I start by documenting the relative importance of *Capital savings* to banks' overall RW. By extending the decomposition method proposed by @cannata2012inside, I find that *Capital savings* accounts for 27% of the RW variation across banks. I also find that *Capital savings* measures are negatively correlated to other RW components. This correlation implies that banks with higher average portfolio riskiness benefit the most from *Capital savings*. Lastly, although banks benefited from higher *Capital savings* as they moved their portfolio from the standardized to the IRB approach (known as the roll-out effect), the intensity of *Capital savings* has, on average, decreased in time. That is, for the same average PD, capital requirements have increased from 2008 to 2018.

I then extend the analysis to investigate the relationship between *Capital savings* and the business cycle. Prior evidence suggests that capital requirements are procyclical: during economic downturns banks tend to deleverage instead of raising capital. However, as credit conditions deteriorate (and banks react to these new credit conditions) the PD distribution and, consequently, the amount of *Capital savings*, also change. A priori, the direction of the business cycle effect on *Capital savings* is ambiguous. At one extreme, if the entire portfolio is equally affected, then there is only a shift of the location parameter of the PD distribution. Because the PD-RW formula elasticity is lower for higher PD estimates, in this scenario *Capital savings* are procyclical. On the other hand, if riskier assets are more sensitive to credit shocks, then capital savings are countercyclical. The ambiguity arises because *Capital savings* can only increase during a recession if the shape of the PD distribution is affected during the cycle.

I find *Capital savings* to be countercyclical. I estimate that a 1.7% GDP growth rate (one standard deviation) decreases *Capital savings* by 0.83 percentage points on average. In other words, banks have to increase capital by 0.83 percentage points to keep their capital ratio constant. The effect is economically significant as it represents a quarter of the capital ratio standard deviation in the sample. In a capital ratio decomposition exercise, I also find that the the cyclicality of *Capital savings* reduces the procyclicality of capital ratios by 11.6%. The results are robust to different measures of the shape component, such as, *Capital savings* in terms of ratios, *Capital savings* in monetary units, and using Gini coefficients.

I further analyse the relationship of the PD distribution moments with GDP growth and find that during economic expansions average PD and PD variance decrease while the PD kurtosis and PD skewness increase. This evidence implies that distributions become more symmetric and with less extreme values during recessions, suggesting a flight to safety behavior by banks. As the recession reduces their existing portfolio credit quality (evidenced by the negative coefficient of average PD) banks respond by reducing risk-taking.

@@

The remainder of this paper is organized as follows. Section 2 describes the capital requirement formula, the *Capital savings* measure, and the hypothesis concerning this measure. Section 3 describes the collected data and analyses the relative importance of *Capital savings* in explaining differences in risk-weights across banks and time. Section 4 presents evidence on the countercyclical feature of *Capital savings*. Finally, section 5 concludes.  
\section{Institutional Background and Hypotheses} \label{sec:background}

@@

Between the two capital requirement components, the average component is a source of the procyclicality as long the relationship between the business cycle and PD is monotonic. Consider again the example shown in Figure \ref{fig:pdmap} with a portfolio containing a safe asset with PD equal to $PD_L$ and a risky asset with PD equal to $PD_H$ in proportions $q$ and $1-q$. In Appendix XX, I show that for $\text{PD} \in (0,0.25)$, $\text{RW}'>0$, $\text{RW}''<0$ and $\text{RW}'''>0$. I also show in Appendix XX that, on average, XX% of assets' PD lies within this range. For simplicity, I assume a constant $\text{LGD}_i=\text{LGD}$. So, the average component for this portfolio is:

@@

Because $\text{RW}'$ is a convex function and Jensen's inequality, if $d\text{PD}_H=d\text{PD}_H=d\text{PD}$ then $d\text{RW}^{s}/d\text{PD}<0$. In this case, *Capital savings* are procyclical, decreasing when PD estimates increase, i.e., during economic downturns. Figure \ref{fig:pdmapcasesym} shows graphically this first case.

Next, consider the case riskier assets are more affected during the business cycles in term of PD, i.e.,  $d\text{PD}_H>d\text{PD}_L$.For simplicity consider the extreme case of $d\text{PD}_H=d\text{PD}$ and $d\text{PD}_L=0$. In this scenario equation \ref{eq:RW_savings_diff} becomes:

\begin{equation}
\label{eq:second_case}
\begin{aligned}
d\text{RW}^{s}
&=(1-q)\bigg[\text{RW}'(q\text{PD}_L+(1-q)\text{PD}_H)-\text{RW}'(\text{PD}_H)\bigg]d\text{PD}\\
\end{aligned}
\end{equation}

Because $\text{RW}''<0$ and $\text{PD}_H>q\text{PD}_L+(1-q)\text{PD}_H$, if $d\text{PD}_H=d\text{PD}$ and $d\text{PD}$ then $d\text{RW}^{s}/d\text{PD}>0$. In this case, *Capital savings* are countercyclical, increasing when PD estimates increase. In other words, the marginal capital requirement decreases during economic downturns. Figure \ref{fig:pdmapcaseassym} shows graphically this second case.

Finally, consider the case where $d\text{PD}_H=d\text{PD}$, $d\text{RW}^{s}=0$ and $dq=0$. Using equation \ref{eq:RW_savings_diff}, we can find $d\text{PD}_L$ satisfying these conditions:

\begin{equation}
\label{eq:third_case}
\begin{aligned}
d\text{PD}_{L}
&=d\text{PD}\frac{(1-q)}{q}\frac{\bigg[\text{RW}'(\text{PD}_H)-\text{RW}'(q\text{PD}_L+(1-q)\text{PD}_H)\bigg]}{\bigg[\text{RW}'(q\text{PD}_L+(1-q)\text{PD}_H)-\text{RW}'(\text{PD}_L)\bigg]}\\
\end{aligned}
\end{equation}

Because $\text{RW}'<0$ and $\text{PD}_H>q\text{PD}_L+(1-q)\text{PD}_H>\text{PD}_L$, both denominator and numerator of equation \ref{eq:third_case} are negative and consequently, $d\text{PD}_L>0$. From the first case we also know that $d\text{PD}_L<d\text{PD}$. Hence, the difference between the impact of the business cycle on riskier and safer assets have to be sufficiently large such that *Capital savings* are countercyclical.

@@

To shed light on the importance of *Capital savings*, I regress all the components of capital ratio on GDP growth rate. The capital ratio decomposition is shown in equation \ref{eq5}. The contribution of each component to the cyclicality of the capital ratio is the ratio of their estimated coefficient to the coefficient for the capital ratio regression. To guarantee that the sum of all effects add up to 100\%, I use in this analysis the non-winsorized data and restrict the sample to banks which I observe their capital ratio. Although the coefficient for *Capital savings* are no longer statistically significant, Table \ref{tab4} shows that *Capital savings* are the only countercyclical component of capital ratios. The economic magnitude is also meaningful: *Capital savings* reduce the procyclicality of capital ratios by 11.6\%.

@@

In panel B of Table \ref{tab:alt} the measure of *Capital savings* in US dollars is rescaled by the amount of EAD in the respective portfolio following equation \ref{eq:measure3}. This measure, therefore, defines *Capital savings* in terms of the usual metric of capital requirements intensity, risk-weights. Although the coefficient on the wholesale portfolio is no longer statistically significant, total *Capital savings* and those coming from corporate portfolios are still statistically different from zero at the 1%  confidence level. The attenuation of the effect on wholesale portfolio appears to come from large, albeit not significant, procyclical *Capital savings* in sovereign portfolios. Moreover, the small and statistically insignificant coefficient in regression 6 reinforces the claim that countercyclical *Capital savings* in the bank portfolio are due to the extensive and not the intensive margin.

@@

According to the theoretical framework presented in section 4.1, an increase in average PD reduces the amount of *Capital savings* if other moments are kept constant. This relationship is illustrated in panel A of Figure \ref{fig:pdmapcases} and empirically tested in Table \ref{tab:moments_contribution}. In all columns of this table average PD is negatively associated with *Capital savings*. Note that, in Table \ref{tab:moments_contribution}, not only the explained but also explanatory variables change across regressions by portfolio $j$.

@@

At the same time, however, using only the evidence provided by the average and variance of the PD distribution, the hypothesis that portfolio reallocation does not impact *Capital savings* cannot be refuted, exactly because the estimated effect of these two moments on *Capital savings* are strongly aligned with the theoretical framework which portfolio reallocation is not present. Consider now a negative shock to a continuous PD distribution, such that we can measure its skewness and kurtosis. It is trivial that the equivalent case with a continuous PD distribution to the scenario in panel A of figure \ref{fig:pdmapcases} wouldn't affect either of these moments. On the other hand, in the second scenario the PD distribution should become more skewed to the right. Even if we think that some assets will become safer during bad times, it is reasonable to expect a larger effect on the right tail than on the left tail of the PD distribution. Consequently, without portfolio reallocation, we should expect the skewness of the PD distribution to be negatively associated with the GDP growth rate.

@@

\section{Additional Results} \label{sec:results}

@@

This paper contributes to understanding the cyclicality and variability of capital requirements by identifying the effects of an unexplored feature of the IRB framework on capital requirements. *Capital savings* due to the shape of PD distribution and the concavity of the IRB formulas are economically relevant. They explain 27% of the RW variation across banks. *Capital savings* are also countercyclical and reduce the procyclicality of RWA by 11.6%.
Hence, the concavity of IRB formulas could be explored to reduce procyclicality of capital regulation.

@@

@@

# Run the models
reg.list <- lapply(formulas, function(x) {
  felm(x, data = filter(bank.data.win, !is.na(log.CAR_gr)))
})

@@

stargazer(reg.list,
          title = "Capital Savings Effect on Capital Ratio Procyclicality",
          table.layout = "n=c=d#-t-as-",
          notes = "\\parbox[t]{16cm}{The table shows estimates for the following model: \\newline \\begin{equation*}\\Delta \\text{Log RWA}_{i,j,t}^{r} = \\beta \\Delta\\text{Log GDP}_{i,t}+\\alpha_{i}+\\alpha_{t}+\\varepsilon_{i,t}. \\end{equation*} \\newline  Each column uses one component of the capital ratio according to equation \\ref{eq:decomposition} as dependent variable. $\\Delta\\text{Log GDP}_{i,t}$ is the real GDP per capita growth rate.  All regressions include bank and year fixed effects. Robust standard errors adjusted for clustering at the country level are reported in parentheses. *, **, and *** indicate statistical significance at the 10\\%, 5\\%, and 1\\% level respectively.}",

@@

\begin{table}[!htbp] \centering  
\caption{PD moments and the Business Cycle}  
\label{tab:moments_cyclicality}
\footnotesize
\begin{tabular}{@{\extracolsep{1pt}}lccccc}
\multicolumn{6}{c}{\parbox[t]{15.8cm}{The table shows estimates for the following model: \newline \begin{equation*}\Delta \text{Y}_{i,t}^{j} = \beta \Delta\text{Log GDP}_{i,t}+\alpha_{i}+\alpha_{t}+\varepsilon_{i,t}. \end{equation*} \newline 
The dependent variable is the change in a PD distribution moment. In panel A the dependent variable is the mean PD, in panel B the variance of PD and in panel C the PD skewness. $\Delta\text{Log GDP}_{i,t}$ is the real GDP per capita growth rate. All regressions include bank and year fixed effects. Robust standard errors adjusted for clustering at the country level are reported in parentheses. *, **, and *** indicate statistical significance at the 10\%, 5\%, and 1\% level respectively.}} \\
[-1.8ex] \\
\hline \\
\end{tabular}\\
\begin{tabular}{@{\extracolsep{1pt}}cccccc}
\multicolumn{6}{c}{Panel A: $\text{Y}=\Delta \text{Mean(PD}_{i,t}\text{)}$} \\
\end{tabular}

@@

\begin{tabular}{@{\extracolsep{1pt}}cccccc}
\\
\multicolumn{6}{c}{Panel B: $\text{Y}=\Delta \text{Var(PD}_{i,t}\text{)}$}
\end{tabular}

@@

\begin{tabular}{@{\extracolsep{1pt}}cccccc}
\\
\multicolumn{6}{c}{Panel C: $\text{Y}=\Delta \text{Skew(PD}_{i,t}\text{)}$}
\end{tabular}

@@

stargazer(reg.list,
          title = "Correlates of Capital Savings",
          table.layout = "n=c=d#-t-as-",
          notes = "\\parbox[t]{17cm}{The table shows estimates for the following model: \\newline \\begin{equation*}\\text{Log RWA}^{s}_{i,t} = \\gamma X_{i,t-1}+\\alpha_{i}+\\alpha_{t}+\\varepsilon_{i,t}. \\end{equation*} \\newline  The first line of the table show the dependent variable in each regression. $\\Delta\\text{Log GDP}_{i,t}$ is the real GDP per capita growth rate. $X_{i,t-1}$ is a vector of independent variables. All regressions include bank and year fixed effects. Robust standard errors adjusted for clustering at the country level are reported in parentheses. *, **, and *** indicate statistical significance at the 10\\%, 5\\%, and 1\\% level respectively.}",

>>>>

To calculate measures of *Capital savings*, information on the distribution of banks' regulatory risk parameters is needed. I hand-collected information on the distribution of credit risk parameters from banks' Pillar-3 reports. As is common in the literature, I calculate *Capital savings* in terms of risk-weighted assets (RWA), which are simply capital requirements times 12.5, or risk-weights (RW), which are RWA divided by assets. The sample consists of 59 large banking groups that have adopted the IRB approach. The dataset covers 15 countries and goes from 2007 to 2018. Data at such granularity is not available in the common balance sheet datasets, and although very detailed, datasets from credit registers are restricted to one country, and may still lack the relevant information.

With this novel dataset, I investigate the relationship between *Capital savings* and the business cycle. Prior evidence suggests that capital requirements are procyclical: during economic downturns banks tend to deleverage instead of raising capital. However, as credit conditions deteriorate (and banks react to these new credit conditions) the PD distribution and, consequently, the amount of *Capital savings*, also change. A priori, the direction of the business cycle effect on *Capital savings* is ambiguous. At one extreme, if the entire portfolio is equally affected, then there is only a shift of the location parameter of the PD distribution. Because the PD-RW formula elasticity is lower for higher PD estimates, in this scenario *Capital savings* are procyclical. On the other hand, if riskier assets are more sensitive to credit shocks, then capital savings are countercyclical. The ambiguity arises because *Capital savings* can only increase during a recession if the shape of the PD distribution is affected during the cycle.

I find *Capital savings* to be countercyclical. I estimate that a 1.6% GDP growth rate (one standard deviation) decreases *Capital savings* by 0.7 percentage points on average. In other words, banks have to increase capital by 0.7 percentage points to keep their capital ratio constant. The effect is also economically significant. In a capital ratio decomposition exercise, I also find that the the cyclicality of *Capital savings* reduces the procyclicality of capital ratios by 23.7%. The results are robust to different measures of the shape component, such as, *Capital savings* in terms of ratios, *Capital savings* in monetary units, and using Gini coefficients.

I further analyse the relationship of the PD distribution moments with GDP growth and find that during economic expansions average PD and PD variance decrease while the PD skewness increase. This evidence implies that distributions become more symmetric and with less extreme values during recessions, suggesting a flight to safety behavior by banks. As the recession reduces their existing portfolio credit quality (evidenced by the negative coefficient of average PD) banks respond by reducing risk-taking.

@@

The remainder of this paper is organized as follows. Section \ref{sec:background describes the capital requirement formula under the IRB approach, why it creates *Capital savings*, and the hypothesis concerning the cyclicality of *Capital savings*. Section \ref{sec:data} describes the collected data and the measures of *Capital savings*. Section \ref{sec:cycle} presents evidence on the countercyclical feature of *Capital savings*. Section \ref{sec:reallocation} tests if *Capital savings* are affected by portfolio reallocation during the business cycle. Section \ref{sec:additional_results} presentes additional results. Finally, section \ref{sec:conclusion} concludes.

\section{Institutional Background and Hypotheses} \label{sec:background}

@@

Between the two capital requirement components, the average component is a source of the procyclicality as long the relationship between the business cycle and PD is monotonic. Consider again the example shown in Figure \ref{fig:pdmap} with a portfolio containing a safe asset with PD equal to $PD_L$ and a risky asset with PD equal to $PD_H$ in proportions $q$ and $1-q$. In Appendix \ref{sec:appendixa}, I show that for $\text{PD} \in (0,0.25)$, $\text{RW}'>0$, $\text{RW}''<0$ and $\text{RW}'''>0$. I also show in \ref{sec:appendixa} that, on average, XX% of assets' PD lies within this range. For simplicity, I assume a constant $\text{LGD}_i=\text{LGD}$. So, the average component for this portfolio is:

@@

Because $\text{RW}'$ is a convex function and Jensen's inequality, if $\text{dPD}_H=\text{dPD}_H=\text{dPD}$ then $\text{dRW}^{s}/\text{dPD}<0$. In this case, *Capital savings* are procyclical, decreasing when PD estimates increase, i.e., during economic downturns. Figure \ref{fig:pdmapcasesymm} shows graphically this first case.

Next, consider the case riskier assets are more affected during the business cycles in term of PD, i.e.,  $\text{dPD}_H>\text{dPD}_L$.For simplicity consider the extreme case of $\text{dPD}_H=\text{dPD}$ and $\text{dPD}_L=0$. In this scenario equation \ref{eq:RW_savings_diff} becomes:

\begin{equation}
\label{eq:second_case}
\begin{aligned}
\text{dRW}^{s}
&=(1-q)\bigg[\text{RW}'(q\text{PD}_L+(1-q)\text{PD}_H)-\text{RW}'(\text{PD}_H)\bigg]d\text{PD}\\
\end{aligned}
\end{equation}

Because $\text{RW}''<0$ and $\text{PD}_H>q\text{PD}_L+(1-q)\text{PD}_H$, if $\text{dPD}_H=\text{dPD}$ and $\text{dPD}$ then $\text{dRW}^{s}/\text{dPD}>0$. In this case, *Capital savings* are countercyclical, increasing when PD estimates increase. In other words, the marginal capital requirement decreases during economic downturns. Figure \ref{fig:pdmapcaseassym} shows graphically this second case.

Finally, consider the case where $\text{dPD}_H=\text{dPD}$, $\text{dRW}^{s}=0$ and $\text{d}q=0$. Using equation \ref{eq:RW_savings_diff}, we can find $\text{dPD}_L$ satisfying these conditions:

\begin{equation}
\label{eq:third_case}
\begin{aligned}
\text{dPD}_{L}
&=\text{dPD}\frac{(1-q)}{q}\frac{\bigg[\text{RW}'(\text{PD}_H)-\text{RW}'(q\text{PD}_L+(1-q)\text{PD}_H)\bigg]}{\bigg[\text{RW}'(q\text{PD}_L+(1-q)\text{PD}_H)-\text{RW}'(\text{PD}_L)\bigg]}\\
\end{aligned}
\end{equation}

Because $\text{RW}'<0$ and $\text{PD}_H>q\text{PD}_L+(1-q)\text{PD}_H>\text{PD}_L$, both denominator and numerator of equation \ref{eq:third_case} are negative and consequently, $\text{dPD}_L>0$. From the first case we also know that $\text{dPD}_L<\text{dPD}$. Hence, the difference between the impact of the business cycle on riskier and safer assets have to be sufficiently large such that *Capital savings* are countercyclical.

@@

To shed light on the importance of *Capital savings*, I regress all the components of capital ratio on GDP growth rate. The capital ratio decomposition is shown in equation \ref{eq:decomposition}. The contribution of each component to the cyclicality of the capital ratio is the ratio of their estimated coefficient to the coefficient for the capital ratio regression. To guarantee that the sum of all effects add up to 100\%, I use in this analysis the non-winsorized data and restrict the sample to banks which I observe their capital ratio. Although the coefficient for *Capital savings* are no longer statistically significant, Table \ref{tab:contribution} shows that *Capital savings* are the only countercyclical component of capital ratios. The economic magnitude is also meaningful: *Capital savings* reduce the procyclicality of capital ratios by 11.6\%.

@@

In panel B of Table \ref{tab:alt} the measure of *Capital savings* in US dollars is rescaled by the amount of EAD in the respective portfolio following equation \ref{eq:RW_savings}. This measure, therefore, defines *Capital savings* in terms of the usual metric of capital requirements intensity, risk-weights. Although the coefficient on the wholesale portfolio is no longer statistically significant, total *Capital savings* and those coming from corporate portfolios are still statistically different from zero at the 1%  confidence level. The attenuation of the effect on wholesale portfolio appears to come from large, albeit not significant, procyclical *Capital savings* in sovereign portfolios. Moreover, the small and statistically insignificant coefficient in regression 6 reinforces the claim that countercyclical *Capital savings* in the bank portfolio are due to the extensive and not the intensive margin.

@@

According to the theoretical framework presented in section 4.1, an increase in average PD reduces the amount of *Capital savings* if other moments are kept constant. This relationship is illustrated in Figure \ref{fig:pdmapcasesymm} and empirically tested in Table \ref{tab:moments_contribution}. In all columns of this table average PD is negatively associated with *Capital savings*. Note that, in Table \ref{tab:moments_contribution}, not only the explained but also explanatory variables change across regressions by portfolio $j$.

@@

At the same time, however, using only the evidence provided by the average and variance of the PD distribution, the hypothesis that portfolio reallocation does not impact *Capital savings* cannot be refuted, exactly because the estimated effect of these two moments on *Capital savings* are strongly aligned with the theoretical framework which portfolio reallocation is not present. Consider now a negative shock to a continuous PD distribution, such that we can measure its skewness and kurtosis. It is trivial that the equivalent case with a continuous PD distribution to the scenario in Figure \ref{fig:pdmapcasesymm} wouldn't affect either of these moments. On the other hand, in the second scenario the PD distribution should become more skewed to the right. Even if we think that some assets will become safer during bad times, it is reasonable to expect a larger effect on the right tail than on the left tail of the PD distribution. Consequently, without portfolio reallocation, we should expect the skewness of the PD distribution to be negatively associated with the GDP growth rate.

@@

\section{Additional Results} \label{sec:additional_results}

@@

This paper contributes to understanding the cyclicality and variability of capital requirements by identifying the effects of an unexplored feature of the IRB framework on capital requirements. *Capital savings* due to the shape of PD distribution and the concavity of the IRB formulas are economically relevant. *Capital savings* are also countercyclical and reduce the procyclicality of RWA by 23.7%.
Hence, the concavity of IRB formulas could be explored to reduce procyclicality of capital regulation.

@@

p_w <- c(0.01, 0.99)        
bank.data.win2 <- bank.data %>% 
  ungroup()%>%
  mutate(year = as.character(year))%>%
  mutate_if(is.numeric,Winsorize,probs = p_w ,na.rm = TRUE)%>%
  group_by(bvdid)%>%
  mutate(year = as.numeric(year))%>%
  mutate_at(vars(matches("log.RWA.r")), .funs = list(n = ~sum(!is.na(.))))

@@

# Run the models
reg.list <- lapply(formulas, function(x) {
  felm(x, data = filter(bank.data.win2, !is.na(log.CAR_gr)))
})

@@

stargazer(reg.list,
          title = "Capital Savings Effect on Capital Ratio Procyclicality",
          table.layout = "n=c=d#-t-as-",
          notes = "\\parbox[t]{16cm}{The table shows estimates for the following model: \\newline \\begin{equation*}\\Delta \\text{Log RWA}_{i,j,t}^{s} = \\beta \\Delta\\text{Log GDP}_{i,t}+\\alpha_{i}+\\alpha_{t}+\\varepsilon_{i,t}. \\end{equation*} \\newline  Each column uses one component of the capital ratio according to equation \\ref{eq:decomposition} as dependent variable. $\\Delta\\text{Log GDP}_{i,t}$ is the real GDP per capita growth rate.  All regressions include bank and year fixed effects. Robust standard errors adjusted for clustering at the country level are reported in parentheses. *, **, and *** indicate statistical significance at the 10\\%, 5\\%, and 1\\% level respectively.}",

@@

\begin{table}[!htbp] \centering  
\caption{PD moments and the Business Cycle}  
\label{tab:moments_cyclicality}
\footnotesize
\begin{tabular}{@{\extracolsep{1pt}}lccccc}
\multicolumn{6}{c}{\parbox[t]{15.8cm}{The table shows estimates for the following model: \newline \begin{equation*}\Delta \text{Y}_{i,t}^{j} = \beta \Delta\text{Log GDP}_{i,t}+\alpha_{i}+\alpha_{t}+\varepsilon_{i,t}. \end{equation*} \newline 
The dependent variable is the change in a PD distribution moment. In panel A the dependent variable is the mean PD, in panel B the variance of PD and in panel C the PD skewness. $\Delta\text{Log GDP}_{i,t}$ is the real GDP per capita growth rate. All regressions include bank and year fixed effects. Robust standard errors adjusted for clustering at the country level are reported in parentheses. *, **, and *** indicate statistical significance at the 10\%, 5\%, and 1\% level respectively.}} \\
[-1.8ex] \\
\hline \\
\end{tabular}\\
\begin{tabular}{@{\extracolsep{1pt}}cccccc}
\multicolumn{6}{c}{Panel A: $\text{Y}=\Delta \text{Log mean(PD}_{i,t}\text{)}$} \\
\end{tabular}

@@

\begin{tabular}{@{\extracolsep{1pt}}cccccc}
\\
\multicolumn{6}{c}{Panel B: $\text{Y}=\Delta \text{Log var(PD}_{i,t}\text{)}$}
\end{tabular}

@@

\begin{tabular}{@{\extracolsep{1pt}}cccccc}
\\
\multicolumn{6}{c}{Panel C: $\text{Y}=\Delta \text{Log skew(PD}_{i,t}\text{)}$}
\end{tabular}

@@

stargazer(reg.list,
          title = "Correlates of Capital Savings",
          table.layout = "n=c=d#-t-as-",
          notes = "\\parbox[t]{17cm}{The table shows estimates for the following model: \\newline \\begin{equation*}\\text{Log RWA}^{s}_{i,t} = \\gamma X_{i,t}+\\alpha_{i}+\\alpha_{t}+\\varepsilon_{i,t}. \\end{equation*} \\newline  The first line of the table show the dependent variable in each regression. $\\Delta\\text{Log GDP}_{i,t}$ is the real GDP per capita growth rate. $X_{i,t-1}$ is a vector of independent variables. All regressions include bank and year fixed effects. Robust standard errors adjusted for clustering at the country level are reported in parentheses. *, **, and *** indicate statistical significance at the 10\\%, 5\\%, and 1\\% level respectively.}",
